---
title: "EDA_of_Upworthy_dataset"
author: "Noah Mott"
date: "11/4/2021"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
mydata<-read.csv('data.csv')
```

```{r}
summary(mydata)
```
The above is a basic summary of the data in the dataset. You'll note that 

```{r}
library(dplyr)
```
```{r}
mydata %>%
  select(everything()) %>%  
  summarise_all(funs(sum(is.na(.))))
```
All Data in the data frame is filled in. This is a good data set for exploration
```{r}
unique(mydata$zip_code)
```
```{r}
unique(mydata$channel)
plot(as.factor(mydata$channel))
```
```{r}
unique(mydata$offer)
plot(as.factor(mydata$offer))

```
We can see in the above unique values that the categorical columns for offer, zip_code, and channel each have 3 categories each. In order to appropriately use them in any sort of regression, we will need to encode the values 1 through 3.

```{r}
plot(as.factor(mydata$zip_code))
```
```{r}
chart1 <- table(as.factor(mydata$zip_code), as.factor(mydata$offer))
chart2<-table(as.factor(mydata$zip_code), as.factor(mydata$channel))
chart3<-table(as.factor(mydata$channel), as.factor(mydata$offer))
```

```{r}
chart1
chart2
chart3
```
```{r}
mydata %>%
        group_by(zip_code) %>%
        tally()
mydata %>%
        group_by(offer) %>%
        tally()
mydata %>%
        group_by(channel) %>%
        tally()
```

```{r}

library(rlang)
library(dplyr)
mydata %>%
        group_by(zip_code, offer, channel) %>%
        tally()

```

Note the above tables indicating the counts for each of the individual categories for the three different categorical variables as well as the counts for each grouping of all three 